Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2016-04-10 Paper/paper.tex
Revisions to paper.

In the UK a variety of utilisation targets are often discussed: aiming to ensure that wards/hospitals operate at a given utilisation value.
The effect of these target policies is investigated justifying their use to align the interests of individual hospitals and social welfare.
In particular, we identify the lowest value of a utilisation target that aligns these.
\end{abstract}

@@

A Critical Care Unit (CCU), also sometimes referred to as an Intensive Therapy Unit or Intensive Therapy Department, is a special ward that is found in most acute hospitals.
It provides intensive care (treatment and monitoring) for people who are critically ill or are in an unstable condition.
CCUs face major challenges, on average, 8\% of patients are refused admission to a CCU because the Unit is full \cite{Report}.
The CCU occupancy rates for some hospitals are reportedly very high \cite{Mitchell1995,Smith1995} and a shortage of beds has been identified throughout the UK.

@@

Throughout this paper it is assumed that both CCUs (NH and RG) act selfishly and rationally.
The strategies of each CCU are capacity thresholds at which they declare being in ``diversion''. When in ``diversion'' the arrival rates of patients are modified.
Given the proximity of the two CCUs, one CCU could for example divert their patients to the other.
Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_H^{r}$ for $H\in\{\NH, \RG\}$ and $r\in\{(l,l), (l,h), (h,l), (h,h)\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $r$ denotes regions with boundaries defined by the capacity thresholds.
For example $(l,h)$ denotes a region for which $\NH$ experiences \textit{low} demand and $\RG$ experiences \textit{high} demand.
It is also assumed that diverted patients will be treated under the length of stay profile of the CCU they are admitted to.
The capacity thresholds are denoted as $K_{H}\in\mathbb{Z}$ for $H\in\{\NH,\RG\}$. Note that $0\leq K_N\leq c_H$.

@@

\begin{figure}[!htbp]
\begin{center}
    \begin{tikzpicture}[scale=.7, every node/.style={scale=0.7}]
        % -----------------------------------------------
        % Boundaries ------------------------------------
        % -----------------------------------------------
        \draw [dashed, line width=1mm, red, opacity=.3] (12,2) -- (12,-20);
        \draw [dashed, line width=1mm, red, opacity=.3] (-2,-12) -- (20,-12);
        %\tikzstyle{state}=[ellipse, draw, fill=blue!10, minimum width=2cm];
        %\tikzstyle{state}=[rectangle, draw, fill=blue!10, minimum width=2cm];
        \tikzstyle{state}=[minimum width=2cm, font=\boldmath];
        %\draw  (0,0) rectangle (4,3);
        %\draw [dashed, red, thick] (0,1) -- (4,1);
        %\draw [dashed, red, thick] (3,0) -- (3,3);
        % -----------------------------------------------
        % First row--------------------------------------
        % -----------------------------------------------
        \node (aa) [state] at (0,0) {$(0,0)$};
        \node (ab) [state] at ($(aa) + (3,0)$) {$(0,1)$};
        \node (ac) [state] at ($(ab) + (3,0)$) {$(0,2)$};
        \node (ellipsisa1) at ($(ac) + (3,0)$) {$\dots$};
        \node(ak) [state] at ($(ellipsisa1) + (3,0)$) {$(0,K_{\RG})$};
        \node (ellipsisa2) at ($(ak) + (3,0)$) {$\dots$};
        \node(az) [state] at ($(ellipsisa2) + (3,0)$) {$(0,c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (aa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ab);
        \draw (aa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ab);

@@

        \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisb1);
        \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisb1);

@@

        \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisc1);
        \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisc1);

@@

        \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisd1);
        \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisd1);

@@

        \draw (ec) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (ellipsise1);
        \draw (ec) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsise1);

@@

        \draw (fc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (ellipsisf1);
        \draw (fc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisf1);

@@

        \draw (zc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (ellipsisz1);
        \draw (zc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisz1);

@@

\hspace{2cm}For all $H\in\{\text{NH}, \text{RG}\}$ minimise:
$$\left(U_{H}-t\right)^2$$
\hspace{2cm}Subject to:
\begin{align}
0\leq & K_H \leq c_{H}\label{model1}\\
&K_H \in  \mathbb{Z}\nonumber
\end{align}

@@

Let $f_{H}(k):[1,c_{\bar H}]\to[1,c_H]$ be the best response of player $H\in\{\NH, \RG\}$ to the diversion threshold of $\bar h\ne h$ ($\bar H\in\{\NH, \RG\}$).

@@

The function $f_H$ is well defined as it maximises a continuous function over a finite discrete set.
In case of multiple values that minimize $U_H$, it is assumed that $f_H$ returns the lowest such value, this is consistent with the PoA being a theoretical upper bound of the effect of uncoordinated behaviour \cite{TimRoughgarden}.

@@

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
            \foreach \x in {0,9}
            {\coordinate (origin) at (\x,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\RG}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at RG};
                % lambda
                \draw ($(origin) + (0,2)$) -- ($(origin) + (2,2)$) -- ($(origin) + (2,4)$) -- ($(origin) + (5,4)$);
                \node at ($(origin) + (1,2.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
                \node at ($(origin) + (3.5,4.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
                % Effect of KRG
                \draw [dashed] ($(origin) + (0,2)$) -- ($(origin) + (4,2)$) -- ($(origin) + (4,4)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,2)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,2)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\RG}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\RG}+1\)};
            };
        \end{tikzpicture}
    \end{center}
    \caption{The effect of \(K_{\RG}\) on \(\bar \lambda\).}\label{fig:effect_of_KRG_on_arrival_rate}
\end{figure}

@@

In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), this gives: \(U_{\NH}(K_{\NH}) = U_{\NH}(\bar \lambda_{\NH}(K_{\NH}) \leq U_{\NH}(\bar \lambda_{\NH}(K_{\NH}+1)) = U_{\NH}(K_{\NH}+1)\) giving:

@@

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
            \foreach \x in {0,9}
            {\coordinate (origin) at (\x,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\NH}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at NH};
                % lambda
                \draw ($(origin) + (0,4)$) -- ($(origin) + (2,4)$) -- ($(origin) + (2,2)$) -- ($(origin) + (5,2)$);
                \node at ($(origin) + (1,3.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
                \node at ($(origin) + (3.5,1.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
                % Effect of KNH
                \draw [dashed] ($(origin) + (0,4)$) -- ($(origin) + (4,4)$) -- ($(origin) + (4,2)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,4)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,4)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\NH}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\NH}+1\)};
            };
        \end{tikzpicture}
    \end{center}
    \caption{The effect of \(K_{\NH}\) on \(\bar \lambda\).}\label{fig:effect_of_KNH_on_arrival_rate}
\end{figure}

@@

\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{\NH}^{(r)}=\begin{cases}
\lambda_{\NH}, &\text{if }r=a\\
\lambda_{\NH}+\lambda_{\RG},  &\text{if }r=b\\
0, &\text{if }r\in\{c,d\}\\
\end{cases}$$}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{\RG}^{(r)}=\begin{cases}
\lambda_{\RG}, &\text{if }r=a\\
\lambda_{\NH}+\lambda_{\RG},  &\text{if }r=c\\
0, &\text{if }r\in\{b,d\}\\
\end{cases}$$}
\end{minipage}

@@

\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{NH}^{(r)}=\begin{cases}
\lambda_{NH}, &\text{if }r\in\{a,d\}\\
\lambda_{NH}+\lambda_{RG},  &\text{if }r=b\\
0, &\text{if }r=c\\
\end{cases}$$}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{RG}^{(r)}=\begin{cases}
\lambda_{RG}, &\text{if }r\in\{a,d\}\\
\lambda_{NH}+\lambda_{RG},  &\text{if }r=c\\
0, &\text{if }r=b\\
\end{cases}$$}
\end{minipage}

>>>>

In the United Kingdom a variety of utilisation targets are often discussed:
aiming to ensure that wards/hospitals operate at a given utilisation value.  The
effect of these target policies is investigated justifying their use to align
the interests of individual hospitals and social welfare.  In particular, we
identify the lowest value of a utilisation target that aligns these.
\end{abstract}

@@

A Critical Care Unit (CCU), also sometimes referred to as an Intensive Therapy Unit or Intensive Therapy Department, is a special ward that is found in most acute hospitals.
It provides intensive care (treatment and monitoring) for people who are critically ill or are in an unstable condition.
CCUs face major challenges, on average, 8\% of patients are refused admission to a CCU because the Unit is full \cite{Report}.
The CCU occupancy rates for some hospitals are reportedly very high
\cite{Mitchell1995,Smith1995} and a shortage of beds has been identified
throughout the United Kingdom.

@@

Throughout this paper it is assumed that both CCUs (NH and RG) act selfishly and rationally.
The strategies of each CCU are capacity thresholds at which they declare being in ``diversion''. When in ``diversion'' the arrival rates of patients are modified.
Given the proximity of the two CCUs, one CCU could for example divert their patients to the other.
Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_H^{r}$ for $H\in\{\NH, \RG\}$ and $r\in\{(l,l), (l,h), (h,l), (h,h)\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $r$ denotes regions with boundaries defined by the capacity thresholds.
For example $(l,h)$ denotes a region for which $\NH$ experiences \textit{low} demand and $\RG$ experiences \textit{high} demand.
It is also assumed that diverted patients will be treated under the length of stay profile of the CCU they are admitted to.
The capacity thresholds are denoted as $K_{H}\in\mathbb{Z}$ for
$H\in\{\NH,\RG\}$. Note that $0\leq K_H\leq c_H$.

@@

\begin{figure}[!htbp]
\begin{center}
    \begin{tikzpicture}[scale=.7, every node/.style={scale=0.7}]
        % -----------------------------------------------
        % Boundaries ------------------------------------
        % -----------------------------------------------
        \draw [dashed, red, line width=1mm, opacity=.3] (12,2) -- (12,-20);
        \draw [dashed, red, line width=1mm, opacity=.3] (-2,-12) -- (20,-12);
        %\tikzstyle{state}=[ellipse, draw, fill=blue!10, minimum width=2cm];
        %\tikzstyle{state}=[rectangle, draw, fill=blue!10, minimum width=2cm];
        \tikzstyle{state}=[minimum width=2cm, font=\boldmath];
        %\draw  (0,0) rectangle (4,3);
        %\draw [dashed, red, thick] (0,1) -- (4,1);
        %\draw [dashed, red, thick] (3,0) -- (3,3);
        % -----------------------------------------------
        % First row--------------------------------------
        % -----------------------------------------------
        \node (aa) [state] at (0,0) {$(0,0)$};
        \node (ab) [state] at ($(aa) + (3,0)$) {$(0,1)$};
        \node (ac) [state] at ($(ab) + (3,0)$) {$(0,2)$};
        \node (ellipsisa1) at ($(ac) + (3,0)$) {$\dots$};
        \node(ak) [state] at ($(ellipsisa1) + (3,0)$) {$(0,K_{\RG})$};
        \node (ellipsisa2) at ($(ak) + (3,0)$) {$\dots$};
        \node(az) [state] at ($(ellipsisa2) + (3,0)$) {$(0,c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (aa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ab);
        \draw (aa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ab);

@@

        \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisb1);
        \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisb1);

@@

        \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisc1);
        \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisc1);

@@

        \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisd1);
        \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisd1);

@@

        \draw (ec) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (ellipsise1);
        \draw (ec) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsise1);

@@

        \draw (fc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (ellipsisf1);
        \draw (fc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisf1);

@@

        \draw (zc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (ellipsisz1);
        \draw (zc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisz1);

@@

\hspace{2cm}For all $H\in\{\text{NH}, \text{RG}\}$ minimise:
$$\left(U_{H}-t\right)^2$$
\hspace{2cm}Subject to:
\begin{align}
0\leq &\; K_H \leq c_{H}\label{model1}\\
&K_H \in  \mathbb{Z}\nonumber
\end{align}

@@

Let $f_{H}(k):[1,c_{\bar H}]\to[1,c_H]$ be the best response of player $H\in\{\NH, \RG\}$ to the diversion threshold of $\bar H\ne H$ ($\bar H\in\{\NH, \RG\}$).

@@

The function $f_H$ is well defined as it maximises a continuous function over a
finite discrete set.  In case of multiple values that minimize $U_H$, it is
assumed that $f_H$ returns the lowest such value, this is consistent with the
Price of Anarchy (PoA) being a theoretical upper bound of the effect of
uncoordinated behaviour \cite{TimRoughgarden}.

@@

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
            \coordinate (origin) at (0,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\RG}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at RG};
                % lambda
                \draw ($(origin) + (0,2)$) -- ($(origin) + (2,2)$) -- ($(origin) + (2,4)$) -- ($(origin) + (5,4)$);
                \node at ($(origin) + (1,2.5)$) {\(\lambda_{\NH}^{(h,l)}\)};
                \node at ($(origin) + (3.5,4.5)$) {\(\lambda_{\NH}^{(h,h)}\)};
                % Effect of KRG
                \draw [dashed] ($(origin) + (0,2)$) -- ($(origin) + (4,2)$) -- ($(origin) + (4,4)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,2)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,2)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\RG}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\RG}+1\)};

            \coordinate (origin) at (9,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\RG}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at RG};
                % lambda
                \draw ($(origin) + (0,2)$) -- ($(origin) + (2,2)$) -- ($(origin) + (2,4)$) -- ($(origin) + (5,4)$);
                \node at ($(origin) + (1,2.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
                \node at ($(origin) + (3.5,4.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
                % Effect of KRG
                \draw [dashed] ($(origin) + (0,2)$) -- ($(origin) + (4,2)$) -- ($(origin) + (4,4)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,2)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,2)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\RG}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\RG}+1\)};
        \end{tikzpicture}
    \end{center}
    \caption{The effect of \(K_{\RG}\) on \(\bar \lambda\).}\label{fig:effect_of_KRG_on_arrival_rate}
\end{figure}

@@

In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}),
this gives: \(U_{\NH}(K_{\NH}) = U_{\NH}(\bar \lambda_{\NH}(K_{\NH})) \leq
U_{\NH}(\bar \lambda_{\NH}(K_{\NH}+1)) = U_{\NH}(K_{\NH}+1)\) giving:

@@

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
            \coordinate (origin) at (0,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\NH}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at NH};
                % lambda
                \draw ($(origin) + (0,4)$) -- ($(origin) + (2,4)$) -- ($(origin) + (2,2)$) -- ($(origin) + (5,2)$);
                \node at ($(origin) + (1,3.5)$) {\(\lambda_{\NH}^{(h,l)}\)};
                \node at ($(origin) + (3.5,1.5)$) {\(\lambda_{\NH}^{(h,h)}\)};
                % Effect of KNH
                \draw [dashed] ($(origin) + (0,4)$) -- ($(origin) + (4,4)$) -- ($(origin) + (4,2)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,4)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,4)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\NH}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\NH}+1\)};

            \coordinate (origin) at (9,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\NH}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at NH};
                % lambda
                \draw ($(origin) + (0,4)$) -- ($(origin) + (2,4)$) -- ($(origin) + (2,2)$) -- ($(origin) + (5,2)$);
                \node at ($(origin) + (1,3.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
                \node at ($(origin) + (3.5,1.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
                % Effect of KNH
                \draw [dashed] ($(origin) + (0,4)$) -- ($(origin) + (4,4)$) -- ($(origin) + (4,2)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,4)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,4)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\NH}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\NH}+1\)};
        \end{tikzpicture}
    \end{center}
    \caption{The effect of \(K_{\NH}\) on \(\bar \lambda\).}\label{fig:effect_of_KNH_on_arrival_rate}
\end{figure}

@@

\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{\NH}^{(r)}=\begin{cases}
\lambda_{\NH}, &\text{if }r=(l,l)\\
\lambda_{\NH}+\lambda_{\RG},  &\text{if }r=(l,h)\\
0, &\text{if }r\in\{(h,l),(h,h)\}\\
\end{cases}$$}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{\RG}^{(r)}=\begin{cases}
\lambda_{\RG}, &\text{if }r=(l,l)\\
\lambda_{\NH}+\lambda_{\RG},  &\text{if }r=(h,l)\\
0, &\text{if }r\in\{(l,h),(h,h)\}\\
\end{cases}$$}
\end{minipage}

@@

\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{NH}^{(r)}=\begin{cases}
\lambda_{NH}, &\text{if }r\in\{(l,l),(h,h)\}\\
\lambda_{NH}+\lambda_{RG},  &\text{if }r=(l,h)\\
0, &\text{if }r=(h,l)\\
\end{cases}$$}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{RG}^{(r)}=\begin{cases}
\lambda_{RG}, &\text{if }r\in\{(l,l), (h,h)\}\\
\lambda_{NH}+\lambda_{RG},  &\text{if }r=(h,l)\\
0, &\text{if }r=(l,h)\\
\end{cases}$$}
\end{minipage}
